### 2023-01-12 definitions.tex
up

\textcolor{red}{Ask the question why use a set of propositions for $SAFE$ and $BAD$ rather than use subsets of the set of configurations ? }

@@

Properties in well-structured transition systems are often given as upward- or downward closed sets [references].
%  Parosh Aziz Abdulla, Karlis Cerans, Bengt Jonsson & Yih-Kuen Tsay (1996): General Decidability Theorems for Infinite-State Systems. In: Proc. LICS 1996, IEEE Computer Society Press, pp. 313–321,
%  Alain Finkel & Philippe Schnoebelen (2001): Well-structured transition systems everywhere! Theor. Comput. Sci. 256(1-2), pp. 63–92, doi:10.1016/S0304-3975(00)00102-X.
Transfering the abstract resilience problems into this framework,
it is therefore reasonable to demand that both propositions, SAFE and BAD, are given by 
upward-closed or 
downward-closed sets.

@@

justification des definitions: si on enlève la condition  an upward-closed set $U$ (extended resilience $U$ qq) reachability reduces to resilience (avec $U=\{x\}$ donc indecidable pour les modèles à reachability indécidable.

et encore: renforcer sur l'hypothèses sur I, J tous les deux clos par le haut+bas.

compute the sets of $(I,J,k)$ st S is resilient.\\
max des I,J possibles \\
remark: $k$-resilienc $\leq$ bounded Resilience $\leq$ Resilience.  AVERIFIER !!!

@@

\"Ozkan goes on to prove that for finite-branching WSTS with strong monotonicity, a basis of $\uparrow \post^*(s)$ is computable for every given state $s$ iff the downward-closed problem is decidable, i.e. given a state $s$ of a WSTS
% in the regarded class 
with strong monotonicity 
and a decidable downward-closed set $J$, it can be decided whether $\exists s' \in J ~ s \to^* s'$ (Proposition~1 in \cite{DBLP:conf/gg/Ozkan22}). The characterization is used to show that Petri nets are $\post^*$ -effective. It is well-known that Petri nets constitute WSTS with storng monotonicity (Thm.~6.1 in \cite{DBLP:journals/tcs/FinkelS01}).
However, the hypothesis that $\uparrow \post^*$ is computable cannot be tested in the WSTS framework.

@@

\begin{proof}
Let us show that Reset VASS and LCS don't enjoy the property that $\uparrow \post^*$ is computable.
Suppose that one are able to compute a finite basis of $\uparrow post^*$ for Reset VASS. Then, one would be able to decide whether $0$ is reachable in counter $i$ by examining if there is some vector $v$ in the basis such that $v(i)=0$. But reachability of $0$ in a counter $i$ is undecidable for Reset VASS. sont WSTS with strong compatibility. et l'accessibilité est undecidable.
$\uparrow post^*$ n'est pas calculable pour les LCS non plus car $\uparrow post^*= \uparrow \downarrow post^*$ n'est pas calculable ???
\textcolor{red}{à relire par Mathieu}
\end{proof}

>>>>

% \textcolor{red}{Ask the question why use a set of propositions for $SAFE$ and $BAD$ rather than use subsets of the set of configurations ? }

@@

Properties in well-structured transition systems are often given as upward- or downward closed sets \cite{DBLP:journals/iandc/AbdullaCJT00, DBLP:journals/tcs/FinkelS01}.
%  Parosh Aziz Abdulla, Karlis Cerans, Bengt Jonsson & Yih-Kuen Tsay (1996): General Decidability Theorems for Infinite-State Systems. In: Proc. LICS 1996, IEEE Computer Society Press, pp. 313–321,
%  Alain Finkel & Philippe Schnoebelen (2001): Well-structured transition systems everywhere! Theor. Comput. Sci. 256(1-2), pp. 63–92, doi:10.1016/S0304-3975(00)00102-X.
Transfering the abstract resilience problems into this framework,
it is therefore reasonable to demand that both propositions, SAFE and BAD, are given by 
upward-closed or 
downward-closed sets.

@@

\textcolor{blue}{
justification des definitions: si on enlève la condition  an upward-closed set $U$ (extended resilience $U$ qq) reachability reduces to resilience (avec $U=\{x\}$ donc indecidable pour les modèles à reachability indécidable.
}

\textcolor{blue}{
et encore: renforcer sur l'hypothèses sur I, J tous les deux clos par le haut+bas.
}

\textcolor{blue}{
compute the sets of $(I,J,k)$ st S is resilient.\\
max des I,J possibles \\
remark: $k$-resilienc $\leq$ bounded Resilience $\leq$ Resilience.  AVERIFIER !!!
}

@@

The author in \cite{DBLP:conf/gg/Ozkan22}
%\"Ozkan
 goes on to prove that for finite-branching WSTS with strong monotonicity, a basis of $\uparrow \post^*(s)$ is computable for every given state $s$ iff the downward-closed problem is decidable, i.e. given a state $s$ of a WSTS
% in the regarded class 
with strong monotonicity 
and a decidable downward-closed set $J$, it can be decided whether $\exists s' \in J ~ s \to^* s'$ (Proposition~1 in \cite{DBLP:conf/gg/Ozkan22}). 
The characterization is used to show that Petri nets are $\post^*$-effective. It is well-known that Petri nets constitute WSTS with strong monotonicity (Thm.~6.1 in \cite{DBLP:journals/tcs/FinkelS01}).
However, the hypothesis that $\uparrow \post^*$ is computable cannot be tested in the general WSTS framework.

@@

\begin{proof}
Let us show that Reset VASS and LCS don't enjoy the property that $\uparrow \post^*$ is computable.
Suppose that one are able to compute a finite basis of $\uparrow post^*$ for Reset VASS. Then, one would be able to decide whether $0$ is reachable in counter $i$ by examining if there is some vector $v$ in the basis such that $v(i)=0$. But reachability of $0$ in a counter $i$ is undecidable for Reset VASS. 
% sont WSTS with strong compatibility. et l'accessibilité est undecidable.
$\uparrow post^*$ n'est pas calculable pour les LCS non plus car $\uparrow post^*= \uparrow \downarrow post^*$ n'est pas calculable ???
\textcolor{red}{à relire par Mathieu}
\end{proof}
